Structural Divergence Analysis

### 2017-05-01 analysis-structure.Rmd
CA vs CM y comparaciones R0s

## mut
dri2.mut = read.csv(dri2.mut.fname, header = T)
site = site.info$site
dri2.mut = dri2.mut[1:length(protein.exp), site]
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

## medium
dri2.medium = read.csv(dri2.medium.fname, header = T)
site = site.info$site
dri2.medium = dri2.medium[1:length(protein.exp), site]
rownames(dri2.medium) = paste("medium", rownames(dri2.medium), sep = "")
```

@@

## dat with means and standard errors
d = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

@@

```{r structure-profiles-CN-comparison}

>>>>

## mut
dri2.mut = read.csv(dri2.mut.fname, header = T)
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

## medium
dri2.medium = read.csv(dri2.medium.fname, header = T)
rownames(dri2.medium) = paste("medium", rownames(dri2.medium), sep = "")
```

@@

## dat with means and standard errors
d = ddply(dat,c("dataset", "site"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

@@

```{r structure-CN-comparison}
